An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2020-04-06 submission1/positive_results_SRs_RRs_submission.Rmd
updated the number of journals currently offering RRs

## Methods to mitigate bias
An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection [for a historical overview, see @Wiseman2019]. 
Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of *p*-hacking via restricted flexibility in data analysis. 
However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias [@Rasmussen2009; @Goldacre2016; but see @Kaplan2015]. 
A more effective safeguard against both publication bias and QRPs is promised by Registered Reports [@Chambers2013; @Nosek2014; @Chambers2015; @Jonas2016]. 
Registered Reports (RRs) are a new publication format with a restructured submission timeline: 
Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal. 
The protocol undergoes peer review, and, if successful, receives "in-principle acceptance", meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results. 
The authors then collect and analyse the data and complete the final report. 
The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (http://cos.io/rr).

>>>>

## Methods to mitigate bias
An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection [for a historical overview, see @Wiseman2019]. 
Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of *p*-hacking via restricted flexibility in data analysis. 
However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias [@Rasmussen2009; @Goldacre2016; but see @Kaplan2015]. 
A more effective safeguard against both publication bias and QRPs is promised by Registered Reports [@Chambers2013; @Nosek2014; @Chambers2015; @Jonas2016]. 
Registered Reports (RRs) are a new publication format with a restructured submission timeline: 
Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal. 
The protocol undergoes peer review, and, if successful, receives "in-principle acceptance", meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results. 
The authors then collect and analyse the data and complete the final report. 
The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known. 
Since its introduction at the journal *Cortex* in 2013, the format has rapidly gained popularity and is offered by 242 journals at the time of writing (http://cos.io/rr).

### 2020-04-06 submission1/positive_results_SRs_RRs_submission.tex
updated the number of journals currently offering RRs

An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias (Goldacre et al., 2016; Rasmussen, Lee, \& Bero, 2009; but see Kaplan \& Irvin, 2015).
A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
Registered Reports (RRs) are a new publication format with a restructured submission timeline:
Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
The authors then collect and analyse the data and complete the final report.
The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 225 journals at the time of writing (\url{http://cos.io/rr}).

>>>>

An increasingly popular proposal to reduce bias is preregistration, where authors register a time-stamped protocol of their hypotheses, planned method, and analysis plan before data collection (for a historical overview, see Wiseman, Watt, \& Kornbrot, 2019).
Preregistration is thought to mitigate QRPs by preventing HARKing (hypotheses must be stated before the results are known) and by reducing the risk of \emph{p}-hacking via restricted flexibility in data analysis.
However, preregistration does not prevent file-drawering or reviewer bias and may thus be insufficient to fight publication bias (Goldacre et al., 2016; Rasmussen, Lee, \& Bero, 2009; but see Kaplan \& Irvin, 2015).
A more effective safeguard against both publication bias and QRPs is promised by Registered Reports (Chambers, 2013; Chambers, Dienes, McIntosh, Rotshtein, \& Willmes, 2015; Jonas \& Cesario, 2016; Nosek \& Lakens, 2014).
Registered Reports (RRs) are a new publication format with a restructured submission timeline:
Before collecting data, authors submit a study protocol containing their hypotheses, planned procedures, and analysis pipeline (typically in the form of an Introduction and Method section) to a journal.
The protocol undergoes peer review, and, if successful, receives \enquote{in-principle acceptance}, meaning that the journal commits to publishing the final article following data collection, regardless of the statistical significance of the results.
The authors then collect and analyse the data and complete the final report.
The final report undergoes another round of peer review, but this time only to ensure that the authors adhered to the registered plan and did not draw unjustified conclusions (and, if applicable, that the data pass pre-specified quality checks).
Registered Reports thus combine an antidote to QRPs (preregistration) with an antidote to publication bias, because studies are selected for publication before their results are known.
Since its introduction at the journal \emph{Cortex} in 2013, the format has rapidly gained popularity and is offered by 242 journals at the time of writing (\url{http://cos.io/rr}).
